---
title: "Meteorite Landings"
author: ""
date: "November 14, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

This comprehensive data set from The Meteoritical Society contains data on all of the known meteorite landings, consisting of 45,716 observations (obtained from <a href="https://data.nasa.gov/Space-Science/Meteorite-Landings/gh4g-9sfh" target="_blank">NASA's Data Portal</a>). It may take some time for the complete map to load.

The diameter of each marker at a landing site is scaled to the mass of its corresponding meteorite. Zoom in to see finer detail of individual landing sites.

```{r pressure, warning=FALSE, echo=TRUE}
library(plotly, warn.conflicts=FALSE, quietly=TRUE)

mLnd <- read.csv("Meteorite_Landings.csv")

hover_text <- paste(mLnd$name,"<br>",
                    mLnd$fall, mLnd$year, "<br>",
                    "Mass:", mLnd$mass, "g"
                    )

plot_ly(data=mLnd, type="scattergeo",
        lon=mLnd$reclong, 
        lat=mLnd$reclat, 
        mode="markers",
        size=mLnd$mass,
        text=hover_text
        )
```

